Analytic Occultation Light Curves in Reflected Light

### 2020-05-02 tex/ms.tex
added fig
better fit
more reasonable sigr

\subsection{Non-Lambertian scatterers}
\label{sec:nonlambertian}
In principle, we can just change $\mathbf{I}$.

@@

Second, we must explicitly model the illumination of the body. We assume the
body is illuminated by a point-like source whose flux measured by the observer
is unity. In this case, the observed intensity at any
point on the surface is proportional to the cosine of the angle $\phi$ between
the incident light and the surface normal. Points for which
$\phi \ge \nicefrac{\pi}{2}$ are unilluminated and
therefore have an intensity of zero.
%
If the point-like illumination source is placed at sky coordinates
$(x_s, y_s, z_s)$ in units of the radius of the illuminated body,
the day/night terminator on the body is a half-ellipse
of semi-major axis unity that is fully described by its (signed) semi-minor
axis,
%
\begin{proof}{}
    \label{eq:b}
    b = -\frac{z_s}{r_s}
    \quad,
\end{proof}
%
where $r_s = \sqrt{x_s^2 + y_s^2 + z_s^2}$ is the distance to the source,
%
and the angle $\theta$ by which its semi-major axis is rotated away from the
$+x$-axis (a frame-dependent quantity, defined below).
Given this formulation, and assuming that
$r_s \gg 1$,
it is straightforward to show that the illumination
$\mathcal{I}$ at a point $(x, y)$ on the projected disk of the body is given
by the function
%
\begin{proof}{}
    \label{eq:illum}
    \mathcal{I}(b, \theta, r_s; x, y)&=
    \text{max}\bigg( 0, I(b, \theta, r_s; x, y) \bigg)
\end{proof}
%
where
%
\begin{proof}{}
    \label{eq:illum_poly}
    I(b, \theta, r_s; x, y) &= \frac{1}{\pi r_s^2}
    \bigg(
    -b_c\sin\theta x + b_c\cos\theta y - bz(x, y)
    \bigg)
\end{proof}
%
with $b_c \equiv \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
A quick note on the normalization of Equation~(\ref{eq:illum_poly}):
if we place the illumination source along the $+z$-axis at $(0, 0, z_s)$,
the body is seen at full phase, so $b = -1$, $b_c = 0$, and
%
\begin{proof}{}
    \mathcal{I}_\text{full}(x, y) = \frac{\sqrt{1 - x^2 - y^2}}{\pi z_s^2}
    \quad.
\end{proof}
%
Integrating this over the full disk, we obtain the reflected flux measured
by the observer if the body has unit spherical albedo,
%
\begin{proof}{}
    \mathcal{f}_\text{full} &=
    \int_{-1}^{1}
    \int_{-\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
    \frac{\sqrt{1 - x^2 - y^2}}{\pi z_s^2}
    \,
    \dd y
    \,
    \dd x
    \nonumber \\[0.5em]
    &= \left(\frac{2}{3}\right) \frac{1}{z_s^2}
    \quad,
\end{proof}
%
recalling that $z_s$ is measured in units of the illuminated body's
radius. The factor of $\nicefrac{2}{3}$ is
precisely the ratio of the geometric albedo to the spherical
albedo of a Lambert sphere \citep[see, e.g.][]{Seager2010}. If we placed
the source at $z_s = 1$, reflection off the illuminated body would increase
the total flux measured at the observer by $\nicefrac{2}{3}$ (since, by
assumption, the source flux at the observer is unity). As a sanity check,
if all radiation incident on the body were instead scattered back toward the
source (and hence toward the observer), $f_\text{full}$ would instead be unity:
the flux at the observer would \emph{double}.
\xxx{Is this explanation satisfactory? Does it make sense?}

@@

@@

>>>>

\subsection{Non-Lambertian scatterers}
\label{sec:nonlambertian}
Just change $\mathbf{I}$. \citep{OrenNayar1994}.

\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/oren_nayar.pdf}
        \oscaption{oren_nayar}{%
            Phase curves for different surface roughness coefficients.
            \label{fig:oren_nayar}
        }
    \end{centering}
\end{figure}
%

\section{Applications}
\label{sec:applications}

\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/io_europa.pdf}
        \oscaption{io_europa}{%
            Occultation of Io by Europa.
            \label{fig:io_europa}
        }
    \end{centering}
\end{figure}
%

@@

Second, we must explicitly model the illumination of the body. We assume the
body is illuminated by a point-like source whose flux measured by the observer
is unity. In this case, the observed intensity at any
point on the surface is proportional to the cosine of the angle $\phi$ between
the incident light and the surface normal. Points for which
$\phi \ge \nicefrac{\pi}{2}$ are unilluminated and
therefore have an intensity of zero.
%
If the point-like illumination source is placed at sky coordinates
$(x_s, y_s, z_s)$ in units of the radius of the illuminated body,
the day/night terminator on the body is a half-ellipse
of semi-major axis unity that is fully described by its (signed) semi-minor
axis,
%
\begin{proof}{}
    \label{eq:b}
    b = -\frac{z_s}{r_s}
    \quad,
\end{proof}
%
where $r_s = \sqrt{x_s^2 + y_s^2 + z_s^2}$ is the distance to the source,
%
and the angle $\theta$ by which its semi-major axis is rotated away from the
$+x$-axis (a frame-dependent quantity, defined below).
Given this formulation, and assuming that
$r_s \gg 1$,
it is straightforward to show that the illumination
$\mathcal{I}$ at a point $(x, y)$ on the projected disk of the body is given
by the function
%
\begin{proof}{}
    \label{eq:illum}
    \mathcal{I}(b, \theta, r_s; x, y)&=
    \text{max}\bigg( 0, I(b, \theta, r_s; x, y) \bigg)
\end{proof}
%
where
%
\begin{proof}{}
    \label{eq:illum_poly}
    I(b, \theta, r_s; x, y) &= \frac{1}{\pi r_s^2}
    \bigg(
    -b_c\sin\theta x + b_c\cos\theta y - bz(x, y)
    \bigg)
\end{proof}
%
with $b_c \equiv \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
A quick note on the normalization of Equation~(\ref{eq:illum_poly}):
if we place the illumination source along the $+z$-axis at $(0, 0, 1)$,
the body is seen at full phase, so $b = -1$, $b_c = 0$, and
%
\begin{proof}{}
    \mathcal{I}_\text{full}(x, y) = \frac{\sqrt{1 - x^2 - y^2}}{\pi}
    \quad.
\end{proof}
%
Integrating this over the full disk, we obtain the reflected flux measured
by the observer if the body has unit spherical albedo,
%
\begin{proof}{}
    \mathcal{f}_\text{full} &=
    \int_{-1}^{1}
    \int_{-\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
    \frac{\sqrt{1 - x^2 - y^2}}{\pi}
    \,
    \dd y
    \,
    \dd x
    \nonumber \\[0.5em]
    &= \frac{2}{3}
    \quad,
\end{proof}
%
which is precisely the geometric albedo of a Lambert
sphere \citep[see, e.g.][]{Seager2010}.

@@

\xxx{NO LONGER TRUE. FIX THIS DEFINITION.}

@@

\xxx{FIX THIS DEFINITION. NO LONGER HOW WE COMPUTE IT.}
